A seamless, client-centric programming model for type safe web applications

### 2014-06-19 paper.tex
Fix Chan code.

\begin{code}
srvHello :: Server RcptList -> Server ()
srvHello remoteRcpts = do
  recipients <- remoteRcpts
  sid <- getSessionID
  liftIO $ do
    rcptMVar <- CC.newEmptyMVar
    CC.modifyMVar recipients $ \cs ->
      return ((sid, rcptMVar):cs, ())
\end{code}

@@

\begin{code}
srvSend :: Server RcptList -> String -> Server ()
srvSend remoteRcpts message = do
    rcpts <- remoteRcpts
    liftIO $ do
      recipients <- CC.readMVar rcpts
      mapM_ (\rcpt -> writeChan rcpt message) recipients
\end{code}

>>>>

\begin{code}
srvHello :: Server RcptList -> Server ()
srvHello remoteRcpts = do
  recipients <- remoteRcpts
  sid <- getSessionID
  liftIO $ do
    rcptChan <- CC.newChan
    CC.modifyMVar recipients $ \cs ->
      return ((sid, rcptChan):cs, ())
\end{code}

@@

\begin{code}
srvSend :: Server RcptList -> String -> Server ()
srvSend remoteRcpts message = do
    rcpts <- remoteRcpts
    liftIO $ do
      recipients <- CC.readMVar rcpts
      mapM_ (flip CC.writeChan message) recipients
\end{code}
